On the Functionality of the Multilayer Perceptron

### 2020-11-25 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesis Paper

@@

\paragraph*{}\textcolor{red}{How do I write an introduction???}

@@

@@

\paragraph*{}This concept stems from the idea that a trained neural network classifier is basing its predictions by generating \textit{decision boundaries} in feature space \cite{Loy,James,Serizel}.

@@

\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James}. In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following steps and requirements:
\begin{enumerate}
\item A suitably sized number of files of reasonable audio quality with normalized amplitudes
\item Audio encoded in a standard, and consistent format
\item A consistent sample rate and bit depth between audio files
\item A consistent number of channels
\end{enumerate}
Note that different projects may require a different set of requirement from preprocessing \cite{Virtanen}. For this project, we have chosen to use the following parameters:
\begin{enumerate}
\item Roughly $18,000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
\item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
\item All audio is sampled at $44,100$ Hz and \textcolor{blue}{Bit depth needed - 16? 24?}
\item All audio has been down-mixed into mono-channel waveforms.
\end{enumerate}

>>>>

\begin{abstract}

\end{abstract}

@@

\paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan}. These signals can take the form of day-to-day topics such as weather measurements, financial reports, or audio-visual media, and extend into disciplines of medicine, physics, and digital signal processing. In all cases, we explore a problem where the task to categorize the sample, or subset of the sample into one of $k$ \textit{bins} called classes \cite{Mierswa,Virtanen,Geron}.

\paragraph*{}For this classification task, we have developed an automated model (called a \textit{classifier}) which can process information from a time-series audio file, and group the file based on it's prediction of what produced the sound in that file. For example, classifying an audio file which contains the waveform of a clarinet sustaining a single note should return the classification prediction of "clarinet" and so forth. This non-trivial task requires developing a model

 Developments in computational efficiency and the age of \textit{Big Data} has lead to a staggering increase in the utilization

@@

\subsection{Feature Space}

\paragraph*{}From each audio file sample, we derive an identical set of $p$ predictors that will be

@@

\paragraph*{}This concept stems from the idea that when a trained neural network classifier makes a prediction, it is doing so based on a set of generated \textit{decision boundaries} \cite{Geron,James}.

@@

\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James,Serizel}. In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following steps and requirements:
\begin{enumerate}
\item A suitably sized number of files of reasonable audio quality with normalized amplitudes
\item Audio encoded in a standard, and consistent format
\item A consistent sample rate and bit depth between audio files
\item A consistent number of channels
\end{enumerate}
Note that different projects may require a different set of requirement from preprocessing \cite{Virtanen}. For this project, we have chosen to use the following parameters:
\begin{enumerate}
\item Roughly $18,000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
\item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
\item All audio is sampled at $44,100$ Hz and \textcolor{blue}{Bit depth needed - 16? 24?}
\item All audio has been down-mixed into mono-channel waveforms.
\end{enumerate}
